Resilience and Home-Space for WSTS

### 2024-01-11 diapo/presentation.tex
up
uo

$\Safe = \{q_0(n) \mid n \in \N\}$, $\Bad$ complement of $\Safe$

@@

$\Safe = \{q_1(0)\} $, $\Bad$ complement of $\Safe$

@@

  $\Safe = \{q_1(0)\} $
   {bounded resilience} hold, $6$-resilience hold

@@

  \begin{definition}[\cite{DBLP:journals/iandc/Finkel90}]
A {\em Well-Behaved Transition System} (WBTS) 
is a FAC$^1$-ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ such that   
%the transition relation $ \rightarrow$ is (upward) compatible with $\leq$, i.e., for all 
%$s_1, t_1 , s_2 \in S$
%	with $s_1 \leq s_2$  and $s_1 \rightarrow t_1$, there exists 
%	$t_2 \in S$ with 
%	$t_1 \leq t_2$ and $s_2 \rightarrow^{*} t_2$.
\end{definition}

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Definitions}

>>>>

$\Safe_1 = \{q_0(n) \mid n \in \N\}$

@@

$\Safe_2 = \{q_1(0)\} $

@@

  $\Safe_2 = \{q_1(0)\} $
   {bounded resilience} hold, $6$-resilience hold

@@

  \begin{definition}[\cite{DBLP:journals/lmcs/BlondinFM17}]
A {\em Well-Behaved Transition System} (WBTS) 
is a FAC$^1$-ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ such that   
%the transition relation $ \rightarrow$ is (upward) compatible with $\leq$, i.e., for all 
%$s_1, t_1 , s_2 \in S$
%	with $s_1 \leq s_2$  and $s_1 \rightarrow t_1$, there exists 
%	$t_2 \in S$ with 
%	$t_1 \leq t_2$ and $s_2 \rightarrow^{*} t_2$.
\end{definition}

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Ideals and effectivity}
